Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-14 thesis/chapters/ch_introduction.tex
Updates throughotu intro. onez models. metals intro. jargon intro.

One of the most common ways to model and understand the stellar populations of galaxies in high-dimensional chemical space is through simplified one-zone (or many-zone) models. This treatment extends back to XXX, where galaxies were treated as closed-box systems of gas and stars with simple approximations such as the instantaneous recycling of metal yields from massive stars and homogenous mixing. While simple, these models have been used extensively to explain the mean evolution of stars in chemical space in individual galaxies.

@@

\subsubsection{Galactic Winds: Metal Retention / Ejection}

@@

@@

Cover (briefly) each enrichment source and dominant production elements.

% maybe a section on our own galaxy

%\subsection{Star Formation and Stellar Feedback}\label{intro:sec:sffb}
%
%As elements are synthesized throughout stellar evolution, any framework for modelling galactic evolution requires an understanding of both where, how, and with what properties stars form in a galaxy.

@@

In the simplest model, supernova feedback is treated as the injection of pure thermal energy (and mass) into the fluid element(s) that are host / closest to the chosen site of a supernova explosion. In self-consistent models of star formation and feedback these sites are usually actual star particles, but this does not have to be the case. The first models which included supernova feedback lacked the spatial / mass resolution to resolve individual (or even collective) SN events. This is the source of the commonly known ``overcooling" problem, whereby too little energy is injected into too much mass such that the affected region only reaches modest temperatures ($T \lessim 10^5$~K, as opposed to $T > 10^7$~K, or so). This temperature is right around the peak of the cooling curve, and thus the energy is rapidly radiated away before the injected energy has any time to make a significant dynamical impact of the galaxy. This is still a problem today in large-box simulations of cosmological volumes which have insufficient resulution to resolve individual SNe. While some of the initial, ad-hoc fixes for this problem (e.g. turning off cooling for some time in SN affected fluid elements, decoupling SN affected SPH particles from the hydrodynamics for some time) are still in use today, some notable advancements have been made to employ some combination of kinetic, momentum, and thermal energy feedback to attempt to capture SNe in a more consistent fashion \citep[e.g.][]{Hopkins2014,Simpson2015,Hopkins2018}.

@@

Stellar winds, in addition to stellar radiation, are a potentially important source of pre-SN feedback that helps regulate star formation in / around the birth clouds of newly formed stars. However, the hot ($T>10^{6}$~K), fast ($v \sim 10^{3}$~km~s$^{-1}$) winds from massive stars \citep{Weaver1977} are challenging to model self-consistently in galaxy-scale simulations. For this reason, there has been comparatively little research on how they affect global galaxy properties, even though some models do include their energy injection in an integrated / approximate fashion \citep[e.g.][]{FIRE}. However, stellar winds, from both massive stars and weaker winds from the AGB phase of low mass stars, are important sources of metal enrichment. For these reasons we do include a simplified model for stellar wind feedback in this disseration.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in experimental simulations where radiation feedback is ignored. It is thus likely subdominant to radiation feedback.}
%
%
%
%\section{Semi-Analytic Models / One-zone Models}
%
%Definitely have a lot here. Motivate need for better understanding of mixing processes in galaxies. \citep{SchonrichWeinberg2019}
%
%

>>>>

%
% 
%
\textbf{Not quite sure if onez models should be its own section:} One of the most common ways to model and understand the stellar populations of galaxies in high-dimensional chemical space is through simplified one-zone (or many-zone) models. This treatment extends back many decades \citep[e.g.][]{Schmidt1963,TalbotArnett1971,Lynden-Bell1975}, where galaxies and their total metal abundance were treated as closed-box systems of gas and stars. Over the interveaning decades these models have improved, including perscriptions for gas outflow (a ``leaky-box") or gas inflow (``accreting box"), or both (a ``bathtub" model, e.g. \cite{FinlatorDave2008,Bouche2010}). The assumptions that go into these models vary dramatically with complexity. Simple models can assume, for example, that long-lived low mass stars do not contribute to metal enrichment while metals from massive stars are instantaneously recylced into the galaxy's gas reservoir (i.e. ignoring stellar lifetimes) or that all metals mix instantly and homogenously. More complex models .

Regardless of the assumptions that go into these models, they are powerful tools used

 with simple approximations such as the instantaneous recycling of metal yields from massive stars and homogenous mixing. While simple, these models have been used extensively to explain the mean evolution of stars in chemical space in individual galaxies.

@@

@@

But first, we note that Astronomy jargon is full of idiosyncrisies. As metioned before, the word ``chemical" in the ``galactic chemical evolution" is a bit of a misnomer. This is commonly applied simply to refer to studies interested in the evolution of metal abundances (either as a whole, or for individual isotopes) in galaxies over time, and less often to the astrochemistry that those elements may participate in. Likewise, ``metals" refers broadly to every element except H and He. Throughout this dissertation we often refer to the metallicity ($Z$) of a galaxy, its gas, or its stars. This quantity represents the total mass fraction of all metals -- and is computed as such in our simulations -- but we note that this is impossible to measure the abundances of all metals in astrophysical contexts outside our own Solar System. The metallicity of our own Sun ($Z_{\odot}$), for example, is still uncertain \citep{Asplund2009}. Instead, most observational works adopt Fe as a proxy for total metallicity in stars (due to its many, strong absorption lines) and O as a proxy in gas abundances (as it is the most abundant metal in the Universe and has convenient, strong emisson lines). These metallicity proxies are commonly reported in some form of normalized abundance ratio. For stellar metallicities, this is given in the form [A/B], where [A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, and $N$ refers to the number of atoms of a given element (usually as [Fe/H]). Confusingly, gas-phase abundances are commonly reported as just log($N_A / N_B$), often with the somewhat arbitrary normalization of 12, or log(O/H) + 12, for example.

@@

@@

In the simplest model, supernova feedback is treated as the injection of pure thermal energy (and mass) into the fluid element(s) that are host / closest to the chosen site of a supernova explosion. In self-consistent models of star formation and feedback these sites are usually actual star particles, but this does not have to be the case. The first models which included supernova feedback lacked the spatial / mass resolution to resolve individual (or even collective) SN events. This is the source of the commonly known ``overcooling" problem, whereby too little energy is injected into too much mass such that the affected region only reaches modest temperatures ($T \lesssim 10^5$~K, as opposed to $T > 10^7$~K, or so). This temperature is right around the peak of the cooling curve, and thus the energy is rapidly radiated away before the injected energy has any time to make a significant dynamical impact of the galaxy. This is still a problem today in large-box simulations of cosmological volumes which have insufficient resulution to resolve individual SNe. While some of the initial, ad-hoc fixes for this problem (e.g. turning off cooling for some time in SN affected fluid elements, decoupling SN affected SPH particles from the hydrodynamics for some time) are still in use today, some notable advancements have been made to employ some combination of kinetic, momentum, and thermal energy feedback to attempt to capture SNe in a more consistent fashion \citep[e.g.][]{Hopkins2014,Simpson2015,Hopkins2018}.

@@

Stellar winds, in addition to stellar radiation, are a potentially important source of pre-SN feedback that helps regulate star formation in / around the birth clouds of newly formed stars. However, the hot ($T>10^{6}$~K), fast ($v \sim 10^{3}$~km~s$^{-1}$) winds from massive stars \citep{Weaver1977} are challenging to model self-consistently in galaxy-scale simulations. For this reason, there has been comparatively little research on how they affect global galaxy properties, even though some models do include their energy injection in an integrated / approximate fashion \citep[e.g.][]{FIRE}. However, stellar winds, from both massive stars and weaker winds from the AGB phase of low mass stars, are important sources of metal enrichment. For these reasons we do include a simplified model for stellar wind feedback in this disseration.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in experimental simulations where radiation feedback is ignored. It is thus likely subdominant to radiation feedback.}

\subsection{Metals in the ISM and CGM of Dwarf Galaxies}

The proximity of Milky Way dwarf galaxy satellites allows us to make some of the most detailed extragalactic stellar abundances measurements.

\subsection{Leo P: A Case Study}

We dedicate this section to a specific Local Group dwarf galaxy, Leo P, as its observed properties motivate the initial conditions of the simulations developed in this dissertation. This galaxy is remarkable for being one of the lowest mass dwarf galaxies with observed, ongoing star formation. It is located at a distance of $\sim$ XXX (cite), and was first discovered in HI (cite). Since then, multiple studies have examined its star formation history (cite), gas phase metal abundance as traced through emission in an HII region (cite), stellar abundances (cite), and, most recently, resolved spectroscopy of both the gas and stars

%
%
%
%\section{Semi-Analytic Models / One-zone Models}
%
%Definitely have a lot here. Motivate need for better understanding of mixing processes in galaxies. \citep{SchonrichWeinberg2019}
%
%
